Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-27 ms.tex
some back of the envelope calcs for read noise in grism ap.

\subsubsection{Grism Aperture}
The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
However, there are no side reference pixels or background regions available on the middle two amplifiers.
Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves.
Without reference pixel subtraction, the grism apertures have standard deviations of 153,000 DN.
Reference pixel subtraction drops this value to 45,000 DN and row-by-row subtraction drops it to 9,000 DN.
For a well depth of 60\%, there are $1.0 \times 10^8$ DN of source counts in an exposure, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!

>>>>

\subsubsection{Grism Aperture}
The NIRCam grism time series are particularly susceptible to 1/f noise because the dispersion direction is parallel to the detector's fast-read direction.
This is visible in Figure \ref{fig:longDarkGrism} where the grism apertures (in red) are parallel to the 1/f noise correlations.
The background subtraction along the spatial direction (vertically) will efficiently remove pre-amplifier offsets from frame to frame and amplifier to amplifier.
However, there are no side reference pixels or background regions available on the middle two amplifiers.
Therefore, the 1/f noise will adversely impact broadband behaviors of the lightcurves.
Without reference pixel subtraction, the grism apertures have standard deviations of 153,000 DN.
Reference pixel subtraction drops this value to 45,000 DN and row-by-row subtraction drops it to 9,000 DN.
For a well depth of 60\%, there are $1.0 \times 10^8$ DN of source counts in an exposure, which amounts to a photon error of 7,400 DN assuming a gain of 1.84.
Therefore, 1/f noise can potentially dominate the error budget for broadband grism time series!
Expressed in ppm, the read noise after processing with row-by-row subtraction is 90 ppm as compared to a photon noise of 74 ppm for a CDS subtraction (2 groups in ramp).

The timescale of most interest to studying atmospheres is the transit duration when trying to assess the stability.
The transit durations for most exoplanets considered is several hours long.
We therefore quantify error source over 1 hour duration.
If the smallest stripe subarray is used, frame time is 0.34 seconds.
For simplicity, assuming a duty cycle of 80\% due to detector resets, there are 8460 frames over which to average read noise.
Therefore, the final read noise is only expected to be 1.4 ppm over a 1 hour timescale if each frame is statistically independent.
